---
title: "LABClassifier"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LABClassifier}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette is on building ...

# Introduction

This package is implemented to stratify patients undergoing Breast Cancer into three subtypes: Luminal, Molecular Apocrine (MA) and Basal. To this end, it uses gene expression (RNA-seq, micro-array, illumina beadchip) of genes being determinant for the sensory/secretory split and Luminal/Apocrine split. We base our hypothesis on cell origin, specialisation and tumorogenesis.

The package proposes a main function 'LABClassifier' (Luminal-Apocrine-Basal Classifier) that returns a data.frame containing predictions for each patient. Note that the function can be used with a single sample.

# Getting started

Install the LABClassifier package

``` r
# install.packages("devtools")
devtools::install_github("ElodieDarbo/LABClassifier")
```

Load the library. 

```{r setup}
library(LABClassifier)
```

# Run LABclassifier

Attached to the package, you find a subset of RNA-seq data (RSEM) from TCGA BRCA samples: TCGA.rsem. 

``` r
data(TCGA.rsem)
LABclassifier(TCGA.rsem,plot=TRUE)
```


